---
title: "lab_8"
author: "Lauren Berny, Adriana Conn, Mavis Gallo, Aubrey Green, & Shawn McWeenie"
date: "11/11/2021"
output: pdf_document
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.height= 8, fig.width= 6.5)

library(tidyverse)
library(janitor)
library(here)
library(rio)
library(dplyr)
library(ggplot2)
library(kableExtra)
library(tinytex)
```


```{r commit_1}
star <- import(here("data", "star.csv"),
  setclass = "tbl_df") %>%
  clean_names()
```


Commit 2

For this lab, we used several packages including @tidyversebib, @janitorbib, @herebib, @riobib, @dplyrbib, @kableExtrabib, and @tinytexbib.

These packages were made possible by the _incredible_ folks such as Hadley Wickham [2016] and [Chung-hong Chan, 2021]. 


```{r commit_3}
star %>%
 group_by(sex, frl) %>%
 summarize(math_mean = mean(tmathss), math_sd = sd(tmathss), rdg_mean = mean(treadss), rdg_sd = sd(treadss)) %>%
 kable(digits = 2,
       booktabs = TRUE) %>%
 kable_styling()
            
```
The table above shows that both boys and girls who received free/reduced lunch tended to score lower on average in math and reading scores compared to boys and girls who did not receive free/reduced lunch.

```{r commit_4}
p <- star %>%
mutate(lunch = if_else(frl == "no", "Paid Meals", "Free/Reduced Price Meals")) %>% 
ggplot(aes(totexp, tmathss)) +
 geom_point(color = "grey") +
 geom_smooth(aes(color = lunch), method = "lm") +
 labs(x = "Teacher Experience (years)", y = "Total Math Scale Score", title = "Relation between teacher experience and math scores", subtitle = "Seperate regression lines displayed by free/reduced price lunch status", colour = "Lunch status")
 
p + theme(legend.position = "bottom")
```

The graph above shows teacher experience does not explain the difference in math scores and lunch status. 

\newpage

# References